Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-05 ms.tex
transition sentence/paragraph between color correction section and global parameter discussion
still working on DIRBE discussion in correlation slope section

@@

In the case of the two-component model, based on a spectrum of \PLANCK~and 
DIRBE correlations slopes, we wish to obtain estimates for six free parameters:
$\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall spectrum 
normalization $n$. The constraints we employ are the correlation slopes of each
of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz), 140$\mu$m 
(2141 GHz) and 240$\mu$m (1250 GHz) relative \PLANCK~857 GHz, with 
\PLANCK~857 GHz considered the independent variable. We will refer to the slope
for band $\nu_i$ as $s_{i,857}$. All of the correlations are performed using 
$1^{\circ}$ smoothed maps. The slopes for \PLANCK~100-545 GHz are taken to be 
those from the relative zero level fits of \ref{sec:relzero}, and are 
illustrated by the dashed red lines in plots of Figure \ref{fig:dip}, right 
column. The 857 GHz slope is taken to be unity by definition. We use the SFD98 
reprocessings of the DIRBE bands. Including 857 GHz, we thus have nine 
correlation slope constraints for six free parameters. Including DIRBE 
140$\mu$m and 240$\mu$m is critical in making this problem sufficiently 
constrained, and also in providing information near the peak of the dust SED at
$\sim$140$\mu$m, which is particularly sensitive to the presence of a single 
versus multiple MBB components. % last sentence mentioning
% that the large number of frequency channels and good coverage of the 
% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??

>>>>

While we ultimately aim to obtain \PLANCK-resolution maps of the spatially 
varying dust temperature and optical depth, we start by applying the 
machinery/formalism thus far developed to reassess the best-fit global 
two-component model parameters in light of the \PLANCK~HFI data.

@@

In the case of the two-component model, based on a spectrum of \PLANCK~and 
DIRBE correlations slopes, we wish to obtain estimates for six free parameters:
$\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall spectrum 
normalization $n$. The constraints we employ are the correlation slopes of each
of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz), 140$\mu$m 
(2141 GHz) and 240$\mu$m (1250 GHz) relative to \PLANCK~857 GHz, i.e. 
$dI_{\nu_i}/dI_{857}$. We will refer to the slope for band $\nu_i$ relative to 
\PLANCK~857 GHz as $s_{i,857}$. The slopes for \PLANCK~100-545 GHz are taken 
to be those derived from the relative zero level fits of $\S$\ref{sec:relzero},
and are illustrated by the dashed red lines in plots of Figure \ref{fig:dip}, 
right column. The 857 GHz slope is by definition unity.

At 1250, 2141 and 3000 GHz, we use the SFD98-reprocessed DIRBE maps. For each
DIRBE band, we determine $s_{i, 857}$ by performing a linear fit to DIRBE as a 
function of \PLANCK~857 GHz, after both have been zodiacal light subtracted and
smoothed to $1^{\circ}$ FWHM, also restricting to the low HI mask of 
$\S$\ref{sec:relzero} (see Figure XX).
% smoothed to 1 degree resolution
% restricted to same low HI mask as in Sect. 3.5.2 analysis
% sentence pointing to figure showing the regressions

Including 857 GHz, we thus have nine correlation slope constraints for six 
free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
this problem sufficiently constrained, and also in providing information near 
the peak of the dust SED at $\sim$140$\mu$m, which is particularly sensitive to
 the presence of a single versus multiple MBB components. % last sentence mentioning
% that the large number of frequency channels and good coverage of the 
% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??

%All of the correlations are performed using 
%$1^{\circ}$ smoothed maps

% need to mention that this is all for the low HI mask !!!!
% should have a three panel figure illustrating linear fits of
